Details of specific functions

### 2024-11-11 inst/gitbook/03_specific-tutorials.Rmd
Update 03_specific-tutorials.Rmd

## These ones however, work but don't use the dist.helper (don't save time)
## The dist.helper is not a function
dispRity(my_data, metric = my.sum.of.dist, dist.helper = dist(my_data))
## The dist.helper is not the correct function (should be dist)
dispRity(my_data, metric = my.sum.of.dist, dist.helper = vegdist)
## The dist.helper is not the correct function (should be just dist)
dispRity(my_data, metric = my.sum.of.dist, dist.helper = stats::dist)
```

>>>>

## These ones however, work but don't use the dist.helper (don't save time)
## The dist.helper is not a function
dispRity(my_data, metric = my.sum.of.dist, dist.helper = dist(my_data))
## The dist.helper is not the correct function (should be dist)
dispRity(my_data, metric = my.sum.of.dist, dist.helper = vegdist)
## The dist.helper is not the correct function (should be just dist)
dispRity(my_data, metric = my.sum.of.dist, dist.helper = stats::dist)
```
<!-- 
## Multi disparity: running disparity analyses on different data

All the options and functions we've covered so far are running disparity analyses assuming that there is one unique trait space (although that trait space can be probabilistic and comprising multiple matrices).

```{r}

    tree <- rmtree(2, 10)
    tree[[1]] <- makeNodeLabel(tree[[1]])
    tree[[2]] <- makeNodeLabel(tree[[2]], prefix = "shnode")
    tree[[1]]$root.time <- max(tree.age(tree[[1]])$ages)
    tree[[2]]$root.time <- max(tree.age(tree[[2]])$ages)
    data <- list(matrix(0, nrow = Ntip(tree[[1]]) + Nnode(tree[[1]]), dimnames = list(c(tree[[1]]$tip.label, tree[[1]]$node.label))),
                 matrix(0, nrow = Ntip(tree[[2]]) + Nnode(tree[[2]]), dimnames = list(c(tree[[2]]$tip.label, tree[[2]]$node.label))))

    ## Test working fine
    test <- dispRity(data, metric = mean, tree = tree)
    plot(test)
    expect_equal(summary(test)$obs.median, 0)
```

 -->
